MCMC convergence diagnostics

### 2023-07-07 src/naomi-simple_mcmc/mcmc-convergence.Rmd
Add logit_phi and log_sigma paris plot to the MCMC, and put into appendix

```{r}
rhats <- bayesplot::rhat(mcmc)
bayesplot::mcmc_rhat(rhats)
(big_rhats <- rhats[rhats > 1.1])
length(big_rhats) / length(rhats)
```

@@

```{r}
ratios <- bayesplot::neff_ratio(mcmc)
bayesplot::mcmc_neff(ratios)
```

@@

data.frame(mcmc_summary) %>%
  tibble::rownames_to_column("param") %>%
  ggplot(aes(x = n_eff)) +
    geom_histogram(alpha = 0.8) +
    labs(x = "ESS", y = "Count")
```

@@

>>>>

```{r}
rhats <- bayesplot::rhat(mcmc)

bayesplot::mcmc_rhat_data(rhats) %>%
  ggplot(aes(x = value, y = parameter, col = description)) +
  geom_segment(aes(yend = parameter, xend = ifelse(min(value) < 1, 1, -Inf)), na.rm = TRUE, alpha = 0.7) +
  scale_color_manual(values = "#E69F00") +
  geom_vline(xintercept = 1.05, linetype = "dashed", col = "grey40") +
  labs(x = "Potential scale reduction factor", y = "NUTS parameter", col = "") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank()
  )

ggsave("rhat.png", h = 3, w = 6.25)

(big_rhats <- rhats[rhats > 1.1])
length(big_rhats) / length(rhats)
```

@@

```{r}
ratios <- bayesplot::neff_ratio(mcmc)

breaks <- c(0, 0.1, 0.25, 0.5, 0.75, 1)

bayesplot::mcmc_neff_data(ratios) %>%
  ggplot(mapping = aes(x = value, y = parameter, color = description)) +
  geom_segment(aes(yend = parameter, xend = -Inf), na.rm = TRUE, alpha = 0.7) +
  scale_color_manual(values = c("#56B4E9", "#009E73", "#E69F00")) +
  geom_vline(xintercept = 0.1, linetype = "dashed", col = "grey40") +
  geom_vline(xintercept = 0.5, linetype = "dashed", col = "grey40") +
  geom_vline(xintercept = 1, linetype = "dashed", col = "grey40") +
  labs(x = "ESS ratio", y = "NUTS parameter", col = "") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank()
  )

ggsave("ratio.png", h = 3, w = 6.25)
```

@@

data.frame(mcmc_summary) %>%
  tibble::rownames_to_column("param") %>%
  ggplot(aes(x = n_eff)) +
    geom_histogram(alpha = 0.8) +
    labs(x = "ESS", y = "Count")

ggsave("ess.png", h = 3, w = 6.25)
```

@@

## Paired PCA parameters

Variation between units can be explained by high correlation and high standard deviation, or low correlation and low standard deviation.
Hence there is an unidentifiabiility here that leads to correlated posteriors.

```{r}
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_as", "logit_phi_alpha_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_as", "logit_phi_rho_as"), diag_fun = "hist", off_diag_fun = "hex")
bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_alpha_a", "logit_phi_alpha_a"), diag_fun = "hist", off_diag_fun = "hex")
(plot <- bayesplot::mcmc_pairs(mcmc, pars = c("log_sigma_rho_a", "logit_phi_rho_a"), diag_fun = "hist", off_diag_fun = "hex"))

ggsave("rho_a.png", plot, h = 4, w = 6.25)
```

## ART attendance
